Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
Lots of changes to CH04

\section{\glsentrytext{AVIS} Measurement set-up}
The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.

@@

In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a mechanical degree-of-freedom of the \gls{AVIS}, i.e.
\begin{enumerate}
  \item the translational velocity in $x$ direction (horizontal),
  \item the translational velocity in $y$ direction (horizontal),
  \item the translational velocity in $z$ direction (vertical),
  \item the rotational velocity around the $x$ axis,
  \item the rotational velocity around the $y$ axis,
  \item the rotational velocity around the $z$ axis.
\end{enumerate}
The axes are indicated in \figref{fig:avis:withAxes}.

@@

In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).
For the other directions, the applied signals (\code{r1} and \code{r2}) were set to $0$.
However, inside the feedback loop, all directions are controlled by the experimental controller $\experimental\Controller$.

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
\begin{equation}
  \experimental\Controller = 
  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
\end{equation}
with
\begin{align}
\experimental\Controller_{\mathrm{tran}} &  \approx 
   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
  \experimental\Controller_{\mathrm{rot}} & \approx 
    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
\end{align}
 as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.

\begin{figure}
\setlength\figurewidth{0.75\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/avis-setup-filters.tikz}
\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

The \gls{AVIS} block (\figref{fig:avis:simulink:avis}), conceptually, contains:
\begin{itemize}
  \item static transformations $(K_{\mathrm{act}}, K_{\mathrm{sens}})$, as derived from first principles in \citep{Rademakers2005MSc}, which translates the sensor and actuator signals to physical velocities at the center of the payload,
  \item logic to communicate with the Quanser Q8 \gls{DAQ} board which is physically connected to the \gls{AVIS}, and
  \item signal conditioning.
\end{itemize}

Specifically, the static transformations of the \gls{AVIS} are given by the following gain matrices~\citep[Appendix A.4]{Rademakers2005MSc}:
\begin{align}
  K_{\mathrm{act}}    & \approx \input{\thisDir/data/avis-setup/actuator-gains.tab.tex}\\
  K_{\mathrm{sens}} & \approx \input{\thisDir/data/avis-setup/sensor-gains.tab.tex}
\end{align}
Note that $K_{\mathrm{act}} \in \RR^{8\times6}$ and hence produces signals for the $8$ actuators on the \gls{AVIS}.
These signals are limited to the range $\pm 5\unit{V}$ before they are sent to the \glspl{DAC} on the Q8 \gls{DAQ} board to avoid overdriving the \glspl{DAC}.

The $6$ velocity signals that are digitized by the Q8 \gls{DAQ} are each filtered to transform the voltage induced in the coils of the geophones on the \gls{AVIS} into a velocity using a filter $F$ with transfer function
\begin{equation}
  F(s) \approx \input{\thisDir/data/avis-setup/sensor-filter.inc.tex}
\end{equation}
which is shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
More information regarding this design is given in \citep[Appendix A.3]{Rademakers2005MSc}.
This filter is discretized automatically by \Simulink for the actual implementation.

@@

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{Simulink model of the AVIS sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}

>>>>

\section{\glsentrytext{AVIS} Measurement set-up}
\label{app:avis-setup}
The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.

@@

In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a mechanical degree-of-freedom of the \gls{AVIS}, i.e. 
\begin{enumerate}
  \item $v_x$: the velocity in $x$ direction (horizontal),
  \item $v_y$: the velocity in $y$ direction (horizontal),
  \item $v_z$: the velocity in $z$ direction (vertical),
  \item $\phi_x$: the angular velocity around the $x$ axis,
  \item $\phi_y$: the angular velocity around the $y$ axis,
  \item $\phi_z$: the angular velocity around the $z$ axis.
\end{enumerate}
The coordinate frame and axes are indicated in \figref{fig:avis:withAxes}.

@@

In the main text, we have simplified this system to consider only $v_z$, the vertical translation (i.e. the third signal).
For the other directions, the applied signals (\code{r1} and \code{r2}) were set to $0$.
However, inside the feedback loop, all directions are controlled by the experimental controller $\experimental\Controller$.

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
This controller was constructed by~\citet{Rademakers2005MSc}
 and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef 
  \begin{cases}
     x[n+1] &= A x[n] + B u_c\\
       y_c    &= C x + D u_c 
  \end{cases}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
\begin{equation}
  \experimental\Controller = 
  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
\end{equation}
with
\begin{align}
\experimental\Controller_{\mathrm{tran}} &  \approx 
   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
  \experimental\Controller_{\mathrm{rot}} & \approx 
    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
\end{align}
 as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.

\begin{figure}[p]
\setlength\figurewidth{0.75\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/avis-setup-filters.tikz}
\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{Simulink model of the AVIS sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}

The \gls{AVIS} block (\figref{fig:avis:simulink:avis}), conceptually, contains:
\begin{itemize}
  \item static transformations $(K_{\mathrm{act}}, K_{\mathrm{sens}})$, as derived from first principles in~\citep{Rademakers2005MSc}, which translates the sensor and actuator signals to physical velocities at the center of the payload,
  \item logic to communicate with the Quanser Q8 \gls{DAQ} board which is physically connected to the \gls{AVIS}, and
  \item signal conditioning.
\end{itemize}

In \citet[Appendix A.4]{Rademakers2005MSc}, linear static relationships are derived to link the velocities at the center of the payload to the corresponding actuator voltages.
This yields the matrix:
\begin{align}
  K_{\mathrm{act}}    & \approx \input{\thisDir/data/avis-setup/actuator-gains.tab.tex}\\
\end{align}
Note that $K_{\mathrm{act}} \in \RR^{8\times6}$ and hence produces signals for the $8$ actuators on the \gls{AVIS}.
These signals are limited to the range $\pm 5\unit{V}$ before they are sent to the \glspl{DAC} on the Q8 \gls{DAQ} board to avoid overdriving the \glspl{DAC}.

The $6$ velocity signals that are digitized by the Q8 \gls{DAQ} are each filtered to transform the voltage induced in the coils of the geophones on the \gls{AVIS} into a velocity using a filter $F$ with transfer function
\begin{equation}
  F(s) \approx \input{\thisDir/data/avis-setup/sensor-filter.inc.tex}
\end{equation}
which is shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
More information regarding this design is given in \citep[Appendix A.3]{Rademakers2005MSc}.
This filter is discretized automatically by \Simulink for the actual implementation.
These velocities are then linked by a linear transformation to the (angular) velocities

@@

\begin{remark}
It should be noted that while the benchmark paper by \citet{Voorhoeve2015SYSID} deals with the same physical \gls{AVIS}, the experimental data of the benchmark is fundamentally different from the data presented here.
\Citet{Voorhoeve2015SYSID} only consider the `physical' \gls{AVIS} with $8$ inputs and $6$ outputs as indicated by the \code{QuanserQ8} block in \figref{fig:avis:simulink:avis} as the system under test.
The measurements of the benchmark data were carried out in open-loop.
Hence, the experimental controller ($\experimental\Controller_{\mathrm{benchmark}} = 0$),the saturations, the filter $F$ and the static matrices $K$ are different.
Moreover, the sample rate of the benchmark data is much higher ($\fs  = 20 \unit{kHz}$) compared to the data in this work ($\fs = 1\unit{kHz}$) thanks to an upgrade of the real-time computer responsible for acquiring the signals.
\end{remark}
